Hydras \& Co.: Formalized mathematics in Coq\\ for inspiration and entertainment

### 2021-10-15 doc/JFLA2022/paper.tex
make table layouts consistent

\begin{table}[ht]
\centering
\footnotesize
\begin{tabular}{|l|l|l|l|l|l|}
\hline
\textbf{Package name} & \textbf{Repository} & \textbf{Index identifier} & \textbf{Version} & \textbf{Spec LOC} & \textbf{Proof LOC}\\
\hline
Pocklington & \href{https://github.com/coq-community/pocklington}{\texttt{pocklington}} & \texttt{coq-pocklington} & \texttt{8.12.0} & 825 & 3,798 \\
\hline
Goedel & \href{https://github.com/coq-community/goedel}{\texttt{goedel}} & \texttt{coq-goedel} & \texttt{8.13.0} & 2,799 & 10,762 \\
\hline
Gaia & \href{https://github.com/coq-community/gaia}{\texttt{gaia}} & \texttt{coq-gaia} & \texttt{1.12} & 28,850 & 124,839 \\
\hline
Hydra-battles & \href{https://github.com/coq-community/hydra-battles}{\texttt{hydra-battles}} & \texttt{coq-hydra-battles} & \texttt{0.5} & & \\
\hline
Addition-chains & \href{https://github.com/coq-community/hydra-battles}{\texttt{hydra-battles}} & \texttt{coq-addition-chains} & \texttt{0.5} & & \\
\hline
Gaia-hydras & \href{https://github.com/coq-community/hydra-battles}{\texttt{hydra-battles}} & \texttt{coq-gaia-hydras} & \texttt{0.5} & & \\
\hline
\end{tabular}
\caption{Current numbers of lines of code for \Hydras packages.}
\label{tbl:loc}
\end{table}

>>>>

\begin{table}[ht]
\centering
\footnotesize
\begin{tabular}{llllll}
\hline
\textbf{Package name} & \textbf{Repository} & \textbf{Index identifier} & \textbf{Version} & \textbf{Spec LOC} & \textbf{Proof LOC}\\
\hline
Pocklington & \href{https://github.com/coq-community/pocklington}{\texttt{pocklington}} & \texttt{coq-pocklington} & \texttt{8.12.0} & 825 & 3,798 \\
Goedel & \href{https://github.com/coq-community/goedel}{\texttt{goedel}} & \texttt{coq-goedel} & \texttt{8.13.0} & 2,799 & 10,762 \\
Gaia & \href{https://github.com/coq-community/gaia}{\texttt{gaia}} & \texttt{coq-gaia} & \texttt{1.12} & 28,850 & 124,839 \\
Hydra-battles & \href{https://github.com/coq-community/hydra-battles}{\texttt{hydra-battles}} & \texttt{coq-hydra-battles} & \texttt{0.5} & & \\
Addition-chains & \href{https://github.com/coq-community/hydra-battles}{\texttt{hydra-battles}} & \texttt{coq-addition-chains} & \texttt{0.5} & & \\
Gaia-hydras & \href{https://github.com/coq-community/hydra-battles}{\texttt{hydra-battles}} & \texttt{coq-gaia-hydras} & \texttt{0.5} & & \\
\hline
\end{tabular}
\caption{Current numbers of lines of code for \Hydras packages.}
\label{tbl:loc}
\end{table}
